---
title: "Prueba"
format: html  
editor: visual
execute: 
  echo: false
  warning: false
bibliography: references.bib
---

## Quarto

#### **Quarto** enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).[@bron2011]

```{r}
#| label: bill-dims-species
#| fig-width: 5
#| fig-asp: 0.618
#| echo: false
#| warning: false
library(palmerpenguins)
library(tidyverse)
library(ggthemes)




penguins %>% 
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm, color = species))+
  geom_point()+
  theme_minimal()+
  scale_color_colorblind()+
  labs(x = "Bill lenght", y = "Bill depth")
```
