---
name: Raymond U. Infante Rosa
surname: 
position: "MSc. Student, Biological Oceanography"
address: "University of Puerto Rico, Mayaguez Campus"
phone:
www: raymondinfante.netlify.app/
email: "raymond.infante@upr.edu"
twitter: 
github: RaymondInfante
linkedin: 
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "MSc. Biological Oceanography", "2021-present", "University of Puerto Rico, Mayaguez campus", "Mayaguez, Puerto Rico",
  "BS.Biology", "2016-2020", "University of Puerto Rico, Aguadilla Campus", "Aguadilla, Puerto Rico",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional Experience

```{r}
library(tibble)
tribble(
  ~ Type, ~ Year, ~ Desc, 
  "Work on tracking Sargassum using Remote Sensing, as analyzing it InSitu. Aditionally I'm in charge of analysis the data from InSitu equipments such as: GER1500, EXO1, Solar Light, Eureka", "2022-Present", "NASA MUREP",
  "Graduate Internship funded by NOAA EPP/MSI: Learned to use Remote Sensing tecnologies to track Pelagic Sargassum as to collect for the study of the microplastic. I also Attended meeting and semminars offered by NOAA EPP/MSI. Finally I got an introduction for analyzing data via coding in R as utilizing SNAP software", "2022", "NOAA Cooperative Science Center in Atmospheric Science and Meteorology (NCAS-M) Fellow",
  "In charge of: Marshsalling airplane, loadind/unloading baggage, pushback and cleaning ", "2021", "Ramp Agent, Wester Aviation ",
) %>% 
  detailed_entries(Type, Year, Desc)
```
```

# Research Experience

```{r}
library(tibble)
tribble(
  ~ Type, ~ Year, ~ Desc, 
  "This research is implementing Ocean Color algorithms for Planet SuperDove Sattelites. For further analyses on Coastal Ocean Color studies.","2022-Present","Ocean Color with Planet Scope",
  "This research is trying to answer if Pelagic Sargassum (*natans* and *fluitas*) can increase microplastic concentrations on superficial water.","2022-Present","Possible contamination of Microplastics due to Pelagic Sargassum",
  "We were in charge of conducting two type of census (linear transect and circular observations), measuring and quantifying *Lobatus gigas*, for further analyses on the best methodology for studying *Lobatus gigas* ", "2022", "*Lobatus gigas* Queen Conch Project",
  "We Counted *Phaethon lepturus* for the annual census of this species in the Caribbean", "2020", "Counting *Phaethon lepturus* in the cliffs of Quebradilla Puerto Rico",
  "We Conclude that the uses of coastal plants, helps the Sand Dune to harden, consequently protecting coastal houses. ", "2019", "Using Coastline Plant to Protect and Harden Sand Dunes ",
) %>% 
  detailed_entries(Type, Year, Desc)
```

# Certifications

```{r}
library(tibble)
tribble(
  ~ Type, ~ Year, ~ Desc, 
  "","2022-Present","FAA part 107 Drone Pilot certificate",
  "","2022-Present","Diver First Aid SSI",
  "", "2022-Present", "Nitrox Diver",
  "Deep Dive, Advance Buoyancy, Underwater Navigation, Boat Diving, Computer Diving", "2022-Present", "Advance Diver",
  "", "2022-Present", "DRNA Navigation License ",
  "Mar-Navigation Academy","2022","Navigation Skills and Safety Course",
  "Certificate of Participation","2021","Marine Debris: Challenge and Opportunity",
  "Certificate of Participation","2021","Tools for the Management of Marine Resources of Puerto Rico",
  "Certificate of Participation","2021","Marine Science and Public Health",
  "University of Puerto Rico, Aguadilla Campus","2021","XX Undergraduate Research Symposium",
  "","2021","MSEIP Undergraduate Mentored Student",
) %>% 
  detailed_entries(Type, Year, Desc)
```

# Associations 

```{r}
library(tibble)
tribble(
  ~ Type, ~ Year, ~ Desc, 
  "Asociation Treasurer", "2022-Present", "Asociacion de Estudiantes de Ciencias Marinas (AECiMa)",
  "Vocal", "2022-Present", "Asociacion de Estudiantes de Ciencias Marinas (AECiMa) ",
) %>% 
  detailed_entries(Type, Year, Desc)
```

# Skills

```{r}
library(tibble)
tribble(
  ~ Type, ~ Year, ~ Desc, 
  "Image Processing using: Seadas, SNAP, Qgis, Acolite","2022-Present","Remote Sensing Data Analysis",
  "Data Analysis using: Base R, Tidyverse, Rmarkdown","2022-Present","R Programming Data Analyst",
  "Drone Photography, Photo Mosaics", "2022-Present", "Aerial and Underwater Photographer",
  "Deep Dive, Advance Buoyancy, Underwater Navigation, Boat Diving, Computer Diving", "2022-Present", "Advance Diver ",
  "Use Affinity Photo for editing, color grading and Color correction. \n Uses Davinci Resolve for video editing ","2022-Present","Photo and Video Editing",
) %>% 
  detailed_entries(Type, Year, Desc)
```